Quantitative Benchmarking for Automatically Generated Conjectures

### 2018-03-12 TEBenchmarkPaper/article.tex
IsaCoSy dies even earlier

The most striking result is how rapidly IsaCoSy's running time increases with
sample size: from size 8 upwards, all runs failed (most timed out, a few aborted
early due to running out of memory). As we found with our preliminary testing,
this increase appears exponential, so even large increases to the timeout would
not produce many more successes.

>>>>

The most striking result is how rapidly IsaCoSy's running time increases with
sample size: from size 7 upwards, all runs failed (most timed out, a few aborted
early due to running out of memory). As we found with our preliminary testing,
this increase appears exponential, so even large increases to the timeout would
not produce many more successes.
